\section{Conference presentations}
\vspace{0.5em}

\begin{enumerate}[{[}1{]}]
  
  \item Hutton, E., G. Tucker, M. Piper, A. Kettner, and I. Overeem
    (2019), The Basic Model Interface 2.0: A standard interface for
    geoscientific numerical models and data, AGU Fall Meeting, San
    Francisco, CA, (poster).
  
  \item McDonald, R., M. Piper, E. Hutton, and S. Markstrom (2019),
    Coupling Hydrologic Models with Data Services in an Interoperable
    Modeling Framework, USGS CDI Workshop, Boulder, CO, (poster,
    lightning talk).

  \item Piper, M., G. Tucker, I. Overeem, A. Kettner, E. Hutton, and
    L. McCready (2018), The CSDMS Model Repository, AGU Fall Meeting,
    Washington, DC, (poster).

  \item Piper, M., E. Hutton, and J. Syvitski (2016), A Python
    Interface for the Dakota Iterative Systems Analysis Toolkit, AGU
    Fall Meeting, San Francisco, CA, (talk).

  \item Piper, M., E. Hutton, I. Overeem, and J. Syvitski (2015),
    {WMT}: The {CSDMS} Web Modeling Tool, AGU Fall Meeting, San
    Francisco, CA, (poster).

  \item Piper, M. (2013), A Rapid Cloud Mask Algorithm for {Suomi}
    {NPP} {VIIRS} {Imagery} {EDRs}, NOAA Satellite Conference, College
    Park, MD, (poster).

  \item Piper, M. (2012), {A Rapid Cloud Mask Algorithm for {Suomi}
    {NPP} {VIIRS} {Imagery} {EDRs}}, AGU Fall Meeting, San Francisco,
    CA, (poster).

  \item Piper, M. (2012), {Using IDL with {Suomi} {NPP} {VIIRS} Data},
    HDF and HDF-EOS Workshop XV, Riverdale, MD, (talk).

  \item Piper, M., B. Justice, A. Borsholm, and A.T. Harris (2011),
    Use of Open Geospatial Consortium (OGC) Standards to Disseminate
    and Access Scientific Data, AGU Fall Meeting, San Francisco, CA,
    (poster).

  \item Piper, M. and J.K. Lundquist (2004), Surface-Layer Turbulence
    during a Frontal Passage, AMS 16th Symposium on Boundary Layers
    and Turbulence, Portland, ME, (talk).

  %% \item Lundquist, J.K., M. Piper, and B. Kosovi{\'c} (2004), TKE
  %%   Budgets and Dissipation Length in Disturbed Boundary Layers, AMS
  %%   16th Symposium on Boundary Layers and Turbulence, Portland, ME,
  %%   (talk).

  \item Piper, M, W. Blumen, and R.L. Grossman (1999), Analysis
    of Dissipation in Fronts, AMS 13th Symposium on Boundary Layers
    and Turbulence, Dallas, TX, (poster).

  \item Piper, M., W. Blumen, and N. Gamage (1998), Hotwire
    Anemometer Measurements of Dissipation Rate in Surface-Layer
    Turbulence, AMS 10th Symposium on Meteorological Observations
    and Instrumentation, Phoenix, AZ, (poster).

  \item Piper, M., W. Blumen, and N. Gamage (1997), Sampling of
    Coherent Structures from Bursts of Dissipation Rate, AMS 12th
    Symposium on Boundary Layers and Turbulence, Vancouver, BC,
    (poster).

  \item Piper, M., W. Blumen, and N. Gamage (1997), Effects of a Dry
    Cold Front Passage on Surface-Layer Turbulence, AMS 12th Symposium
    on Boundary Layers and Turbulence, Vancouver, BC, (talk).

  \item Piper, M., J.C. Wyngaard, W.H. Snyder, and R.E. Lawson (1995),
    Convection Tank Experiments on Top-Down, Bottom-Up Diffusion, AMS
    11th Symposium on Boundary Layers and Turbulence, Charlotte, NC,
    (talk).

\end{enumerate}
